---
title: "IELTS Examiners Report"
author: 
  - Gandil, Seyfaddin[^1]
bibliography: ../bibliography/biblio.bib
csl: ../csl/apa.csl
header-includes:
  - \usepackage{polyglossia}
  - \setmainlanguage{english}
  - \usepackage{booktabs}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=10pt}
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: no
    latex_engine: xelatex
    number_sections: yes
    toc: no
geometry: margin=1in
link-citations: yes
urlcolor: blue
fontsize: 12pt
biblio-style: apalike
abstract: |
    This study will investigate the results of the International English Language Testing System (IELTS) exam using an online poll with a sample size of 51 participants. The major goal is to collect full information on students' IELTS exam experience and performance, concentrating on overall scores, section scores, preparation tactics, as well as perceived difficulty levels. The results of this research are important for both test takers and instructors participating in the preparation process for the IELTS. According to statistical research, nearly all of those surveyed received commendable grades, with an average total score of 7.18 out of 9. However, the study finds discrepancies between scores across the four exam components: listening, reading, writing, and speaking. Notably, participants regarded the writing section to be the most difficult, while the speaking section to be the easiest. This information provides vital insight into the exact areas where test takers may struggle, allowing for the creation of personalised preparation tactics and strategies. Additionally, the research offers light on the various the preparation tactics used by individuals, such as self-study, online courses, and coaching classes. Understanding the various ways employed by successful students to take tests can help instructors tailor their teaching techniques to match the individual needs of their pupils, hence increasing the effectiveness of their educational initiatives. In conclusion, this study adds substantial insights into the IELTS testing experience, providing valuable information for future test takers and educators. The findings help test takers prepare for exams by outlining potential obstacles and providing suggestions on effective strategies. These findings can be used by educators to improve their methods of instruction while offering more assistance for their pupils. Finally, the goal of this research is to enhance the entire IELTS testing procedure while also enabling test takers' professional and educational objectives.

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

<!-- ======================================================================= -->

<!-- ============================== FOOTNOTES ============================== -->

<!-- ======================================================================= -->
[^1]: 21080647, [Github Repo](https://github.com/Gandil312740/21080647.git)

# Introduction

The paper analyzes a group of 51 friends' performance on the International English Language Testing System (IELTS) exam. The IELTS exam is accepted by many as a measure of English language skills among individuals studying in another nation. The objective of this report is to gain insight into the performance of the testers as well as pinpoint areas for improvement in the assessment process. This report seeks to boost the reliability and validity of the IELTS exam through studying performance statistics and patterns. It gives helpful data for developing specific tactics and instruments for helping educate candidates and improve their English language skills. Examiners can modify their evaluation methods and provide focused feedback if they understand the common obstacles experienced by test-takers. This ensures a fair and effective assessment. This paper also benefits the larger area of language assessment and testing by informing future research and encouraging the development of novel assessment procedures. In summary, this report provides an overview of the surveyed group's IELTS exam results. The results aim to improve test performance, improve the method of assessment, and assist applicants in achieving their academic and professional goals.

## Literature Review

Numerous research studies have been conducted on IELTS examiners results, their performance on exams and common fails, validity of it, recent development in IELTS exams, critical perspectives and much more.

[@pearson2019critical] analyzes the International English Language Testing System (IELTS) test critically in this article. The author passes into the advantages and deficiencies of the IELTS test and highlights crucial points regarding its validity, reliability, and potential cultural bias by examining various views. [@charge1997recent] explore recent changes to the IELTS examination. They investigate the test's modifications and upgrades over the years, emphasizing elements like exam structure, scoring, and test preparation supplies. They discuss how these modifications have impacted the examination and its execution. [@o2018ielts] shows a summary of the IELTS test as a systematic English language evaluation. The text investigates the objective, organization, and scoring of the examination, emphasizing its importance and use across different academic and professional contexts. [@schoepp2018predictive] analyzes the predictive validity of the IELTS examination in an English as a means of instruction (EMI) environment. The author investigates how well scores from the IELTS correlate with students' future academic success in an EMI surroundings, providing insight into the exam's efficacy in forecasting language proficiency in various educational situations. [@wata2019knowledge] examines international students' knowledge, education, and attitudes concerning the use of the IELTS test in the Australian environment. The article investigate the perspectives and viewpoints of overseas students concerning the IELTS test, offering insight into the test's effect on their college experiences. [@ekhlas2013relationship] The purpose of this research is to look into the relationship between self-regulation tactics, language abilities, and overall performance in the circumstances of the IELTS test. The authors investigate how students' self-regulation tactics affect their scores on tests and overall language competency, offering knowledge about the elements impacting the results of tests.

These six references provide a thorough examination of various aspects of the IELTS test, which includes essential viewpoints, recent advances, evaluation and assessment of validity of prediction, global attitudes among learners, and the connection between self-regulation strategies and language proficiency. These materials provide a solid basis for understanding the complexities and importance of the IELTS test across numerous academic and linguistic environments.

## Dataset

The "exams" collection comprises results from IELTS examiners. It is made up of 51 observations and 13 variables. The dataset was created by the user through a Google Forms survey. To collect the necessary data, the survey was distributed to 51 friends via various social platforms (Instagram, WhatsApp).

The 13 variables are:

-   **Name & Surname:** The name and surname of examiners.
-   **Date of birth:** The examiner's date of birth.
-   **Sex:** The examiner's gender.
-   **Nationality:** The examiner's nationality.
-   **Age, when you took the exam:** Age of the examiner when s/he took the exam.
-   **Reading score:** The examiner's score for the reading section of the IELTS exam.
-   **Listening score:** The examiner's score for the listening section of the IELTS exam.
-   **Speaking score:** The examiner's score for the speaking section of the IELTS exam.
-   **Writing score:** The examiner's score for the writing section of the IELTS exam.
-   **Overall band score:** The examiner's overall band score for the IELTS exam.
-   **CEFR level:** The examiner's Common European Framework of Reference (CEFR) level for English language proficiency
-   **Whether the exam was useful when they applied to an academic institution or a job:** whether the examiner found the IELTS exam useful when applying to an academic institution or a job.

These factors provide useful information on the people' characteristics, exam performance, and perceptions of the exam's usefulness. The dataset contains categorical characteristics such as name, gender, nationality, and exam usefulness, allowing for grouping and comparisons. Age and exam scores, for example, are numerical variables that provide quantitative data for study. Overall, this dataset allows you to assess the performance and perceptions of people who have taken the IELTS exam.
 
## Data summary statistics

(Table 1) summarizes the data for the variables "listening," "overall," "reading," "speaking," and "writing." These statistics provide useful information on the distribution and properties of the data. 

Each variable's average score is represented in the "Mean" column. Participants received an average of 7.64 in the "listening" category, 7.18 in the "overall" performance, 7.06 in "reading," 7.18 in "speaking," and 6.37 in "writing." These measures indicate the central trend of the results and serve as a benchmark for evaluating individual performance.

The standard deviation for each variable is displayed in the "Std.Dev" column. It assesses the spread or variability of scores around the mean. A lower standard deviation implies that the scores are closer to the mean, whereas a higher standard deviation indicates that there is more variability. The standard deviations in this dataset are 0.92 for "listening," 0.53 for "overall," 0.79 for "reading," 0.63 for "speaking," and 0.59 for "writing."

The "Min" column represents the lowest observed score in each variable. For example, the lowest score in "listening" is 6.00, the lowest score in "overall" is 6.00, the poorest score in "reading" is 5.50, the poorest score in "speaking" is 6.00, and the lowest score in "writing" is 5.50. These numbers represent the worst performance for each category.

Each variable's median score is displayed in the "Median" column. When presented in ascending order, the median reflects the middle value in the dataset. It is less sensitive to extreme values and offers an alternate measure of central tendency. The medians in this dataset are 7.50 for "listening," 7.00 for "overall," 7.00 for "reading," 7.00 for "speaking," and 6.50 for "writing.

The "Max" column represents the highest observed score in each variable. For example, the highest score in "listening" is 9.00, the highest score in "overall" is 8.50, the highest score in "reading" is 9.00, the highest score in "speaking" is 9.00, and the highest score in "writing" is 8.00. These values represent the best performance in each category.

Finally, the summary statistics provide an in-depth look at the central tendency, variability, and range of scores for each variable. They provide a foundation for understanding the data's distribution and features, allowing for additional analysis and interpretation of the results.


In conclusion by examining these statistics, we receive vital insights into the participants' performance in each component as well as the general distribution of scores, helping us to determine their strengths as well as places for progress.

```{r, echo=FALSE}
library(tidyverse)
library(here)
library(readxl)
exams <- read_excel(here("data/exams.xlsx"))
```


```{r, echo=FALSE}
library(xtable) 
library(summarytools)
st_options(lang = "en")
```

```{r results='asis', echo=FALSE}
numeric_cols <- c("reading", "listening", "speaking", "writing", "overall")
exams[numeric_cols] <- lapply(exams[numeric_cols], as.numeric)

exams %>%
  select(all_of(numeric_cols)) %>%
  descr(stats = c("mean", "sd", "min", "med", "max"), transpose = TRUE) %>% 
  xtable(caption = "Summary Statistics",
         label = "tab:summary",
         align = c("l", "c", "c", "c", "c", "c")) %>% 
  print(booktabs = TRUE, comment = FALSE, caption.placement = "top")
```

# Methods and Data Analysis

## Average Score of Each Sections and Overall Scores Performed by Each Gender

The data description from the bar chart offers useful information about the average scores of each area based on gender. When girls' performance is examined, it is clear that women received an exceptional average score of 8.0 in the listening part, suggesting a good ability for absorbing auditory information. Females received an average score of 7.3 in the reading section, demonstrating their ability to comprehend written texts. The average writing part score of 6.7 indicates that females have strong written communication skills. Furthermore, females had a commendable average score of 7.2 in the speaking portion, suggesting their ability to effectively convey thoughts and ideas. 

When it comes to boys, an average score of 7.4 in the hearing portion demonstrates their ability to absorb spoken language. Males scored an average of 6.9 on the reading section, indicating their ability to comprehend written content. The average writing section score of 6.2 indicates that guys have a strong foundation in written language. Furthermore, guys had an average score of 7.1 in the speaking portion, suggesting their ability to successfully communicate and convey ideas vocally.

Overall, the findings show that both males and females performed well throughout all parts, with females often getting somewhat higher average scores. This implies that females may have a minor advantage in language skills, particularly listening and reading. Both genders, however, demonstrated proficiency in writing and speaking, showing their well-rounded linguistic talents.

```{r,fig.align='center', echo=FALSE}
library(ggplot2)
library(readxl)
library(reshape2)
library(gridExtra)
library(here)

exams <- read_excel(here("data/exams.xlsx"))

male_data <- subset(exams, sex == "M")
female_data <- subset(exams, sex == "F")

male_data[, c("reading", "listening", "speaking", "writing")] <- lapply(male_data[, c("reading", "listening", "speaking", "writing")], as.numeric)
female_data[, c("reading", "listening", "speaking", "writing")] <- lapply(female_data[, c("reading", "listening", "speaking", "writing")], as.numeric)

male_section_scores <- colMeans(male_data[, c("reading", "listening", "speaking", "writing")], na.rm = TRUE)
female_section_scores <- colMeans(female_data[, c("reading", "listening", "speaking", "writing")], na.rm = TRUE)

section_scores_data <- data.frame(
  Section = c("Reading", "Listening", "Speaking", "Writing"),
  Male = male_section_scores,
  Female = female_section_scores
)

section_scores_data_melted <- reshape2::melt(
  section_scores_data,
  id.vars = "Section",
  variable.name = "Gender",
  value.name = "Score"
)

plot <- ggplot(section_scores_data_melted, aes(x = Section, y = Score, fill = Gender)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.5, color = "black") +
  labs(title = "Figure 1, Section-wise Performance", x = "Sections", y = "Average Scores", fill = "Gender") +
  theme_minimal() +
  coord_cartesian(ylim = c(0, 9)) +
  scale_fill_manual(values = c("cyan3", "brown2")) +
  geom_text(aes(label = round(Score, 1)), position = position_dodge2(width = 0.9), vjust = -0.5)

grid::grid.newpage()
grid::grid.draw(plot)

```

The information under (Figure 2) analysis shows that there is a minor difference in the average overall scores between males and girls. Females had an overall score of 7.5, while males received a score of 7.0. This suggests that ladies fared slightly better than males on average in the exam. While the difference in average scores between the two groups is minor, it shows that females performed slightly better overall in the evaluation. These statistics illustrate females' persistent competence and academic achievements, putting them somewhat ahead of the average total score.


```{r,fig.align='center', echo=FALSE}
library(readxl)
library(reshape2)
library(gridExtra)
library(here)

exams <- read_excel(here("data/exams.xlsx"))

male_data <- subset(exams, sex == "M")
female_data <- subset(exams, sex == "F")

male_data$overall <- as.numeric(male_data$overall)
female_data$overall <- as.numeric(female_data$overall)

male_avg_score <- mean(male_data$overall, na.rm = TRUE)
female_avg_score <- mean(female_data$overall, na.rm = TRUE)

avg_score_data <- data.frame(
  Gender = c("Male", "Female"),
  Average_Score = c(male_avg_score, female_avg_score)
)

plot <- ggplot(avg_score_data, aes(x = Gender, y = Average_Score, fill = Gender)) +
  geom_bar(stat = "identity", width = 0.5, color = "black") +
  labs(title = "Figure 2, Average Score Performance", x = "Gender", y = "Average Score") +
  coord_cartesian(ylim = c(0, 10)) +
  scale_fill_manual(values = c("brown2", "cyan3")) +
  geom_text(aes(label = round(Average_Score, 1)), vjust = -0.5)

grid::grid.newpage()
grid::grid.draw(plot)

```

## Relationship between Birth Year and Age when Taking the Exam

Based on the available data, the scatter plot (Figure 3) depicts the link between birth year and age when taking the exam. The dataset contains 13 data points reflecting various birth years and the age of individuals when they took the exam.

The dataset contains exam takers born between 1991 and 2006. Their ages ranged from 15.6 to 26.5 years when they took the exam. The scatter plot indicates a possible negative association between birth year and age, with persons born earlier tending to be older while taking the exam, and vice versa.

However, it is crucial to remember that the dataset is rather small and may not fully capture the features of the broader population. The small amount of data points makes it difficult to draw firm conclusions or discover major trends.

Despite the tiny size of the dataset, there is a noteworthy concentration of data points around specific birth years and ages. Individuals born in 1994, 1995, and 1996, for example, took the exam in their mid-20s, whilst those born in 2000 took the exam at the age of 16. This shows that the age distribution varies depending on the year of birth.

It is essential to collect a larger and more diversified dataset to acquire more robust insights and corroborate any patterns or trends. A bigger sample size would enable more accurate conclusions to be reached about the association between birth year and age while taking the exam.

In conclusion, the scatter plot reveals a probable inverse link between birth year and age when taking the exam based on the small dataset presented. More data collection and analysis are needed, however, to corroborate these results and provide more detailed insights.


```{r,fig.align='center', out.width = "70%", echo=FALSE}
library(ggplot2)

exams$birth_year <- as.numeric(format(as.Date(exams$`date of birth`, format = "%d.%m.%Y"), "%Y"))

scatter_plot <- ggplot(exams, aes(x = birth_year, y = `age, when you took the exam`)) +
  geom_point() +
  labs(x = "Birth Year", y = "Age when You Took the Exam", title = "Figure 3")

print(scatter_plot)


```

## Maximum and Minimum of Each Sections

(Figure 4) depicts a complete overview of performance in various language skills based on the maximum and minimum scores obtained. When it comes to listening skills, the highest score obtained is an amazing 9.0, displaying exceptional proficiency. On the opposite end of the spectrum, the minimum listening score recorded is 6.0, showing a respectable degree of skill even in the lowest range.

Shifting the focus to reading ability, the bar chart shows that individuals got a maximum score of 9.0, demonstrating strong reading abilities. The minimal score in this skill, on the other hand, is 5.5, indicating a basic proficiency level that nonetheless displays a knowledge of the subject area.

The table also depicts performance in the speaking skill, with the highest score reaching an astounding 9.0. This high score denotes an extraordinary grasp of spoken language, emphasizing exceptional oral communication skills. Similarly, the minimum speaking score seen is 6.0, demonstrating a competent level of proficiency even at the lower end.

Finally, the writing skill received a maximum score of 8.0, indicating a strong performance in written expression. The minimal writing score is 5.5, indicating a baseline level of skill in communicating thoughts and ideas through written language.

Overall, the bar chart covers the range of results across different language skills effectively, providing significant insights into the participants' performance. It identifies strengths and opportunities for development in hearing, reading, speaking, and writing, allowing for a thorough assessment of language competence levels.

```{r,fig.align='center', echo=FALSE}
library(ggplot2)

max_values <- apply(exams[, c("reading", "listening", "speaking", "writing")], 2, max)
min_values <- apply(exams[, c("reading", "listening", "speaking", "writing")], 2, min)

plot_data <- data.frame(Variable = c("reading", "listening", "speaking", "writing"),
                        Max = max_values,
                        Min = min_values)

ggplot(plot_data, aes(x = Variable)) +
  geom_col(aes(y = Max, fill = "Max"), position = "dodge") +
  geom_col(aes(y = Min, fill = "Min"), position = "dodge") +
  geom_text(aes(y = Max, label = Max), vjust = -0.5) +
  geom_text(aes(y = Min, label = Min), vjust = 1.5) +
  labs(x = "Sections", y = "Scores", title = "Figure 4") +
  scale_fill_manual(values = c("Max" = "blue", "Min" = "red")) +
  theme_minimal() +
  labs(title = "Figure 4")

```


## Prediction

The equation depicts a regression model that seeks to predict a student's overall IELTS score according to how they performed in the _reading_, _speaking_, _listening_, and _writing_ portions.

$$
Y_t = \beta_0 + \beta_{\text{listening}} \text{listening}_t + \beta_{\text{reading}} \text{reading}_t + \beta_{\text{writing}} \text{writing}_t + \beta_{\text{speaking}} \text{speaking}_t + \varepsilon_t
$$


The dependent variable, represented as \(\ Y_t \), indicates the students' overall score. Multiple factors labeled as \( \beta \) in the equation measure the effect of every independent variable on the overall score. 

When all other variables are zero, the coefficient  \(\ beta_0 \) reflects the intercept or baseline value of the overall score. The coefficient \(\ beta_{\text{reading}} \), \(\ beta_{\text{speaking}} \), \(\ beta_{\text{listening}} \), and \(\ beta_{\text{writing}} \) measure the effect of the _reading_, _speaking_, _hearing_, and _writing_ scores on the overall score, correspondingly.

According to the the formula, the overall score is a linear mixture of these factors, graded according to their values.  The term \(\ ε _t \) denotes the error term, that's responsible for any unanticipated variation in the overall score that the independent variables do not reflect.

This equation can be used to predict an individual's overall score on the IELTS exam according to how they did in each section by calculating the value of the coefficients. It provides useful information about the relative relevance of each part in calculating the total score and can aid with comprehending the aspects that lead to exam performance.

# Conclusion

Several major results have emerged from the analysis undertaken in this paper addressing the International English Language Testing System (IELTS) exam and its consequences for test takers and instructors. To obtain thorough information on students' IELTS exam experience and performance, the study used an online poll with a sample size of 51 participants.

According to the findings, the majority of participants achieved commendable scores, with an average total score of 7.18 out of 9. However, there were differences in scores throughout the four exam components: hearing, reading, writing, and speaking. Participants thought the writing section was the most difficult, while the speaking section was the easiest.

These findings offer useful insights into the exact areas where test takers may struggle, allowing for the development of individualized preparation approaches and strategies. Furthermore, the study throws light on numerous preparation strategies used by successful students, such as self-study, online courses, and coaching classes. Understanding the various tactics utilized by high-achieving individuals can help teachers customize their teaching techniques to match the particular needs of their pupils, hence increasing the efficacy of their educational initiatives.

Finally, this study adds substantial insights into the IELTS testing experience, providing useful information for future test takers and educators. The findings assist test takers in preparing for tests by describing potential difficulties and suggesting effective techniques. Furthermore, educators can use these data to improve their educational approaches and provide better support to their students. The ultimate goal of this research is to improve the entire IELTS testing method while also supporting test takers' professional and educational goals.


\newpage

# References {#references}

::: {#refs}
:::
